\chapter{Extension}
\label{sec_ext}

LaBoGrid's configuration file, described in chapter~\ref{sec_conf}, contains
references to classes whose implementation is provided by LaBoGrid. However,
most of them can be replaced by classes provided by the user. For example,
one may want to use its own collision operator. In this case, it can
implement its own collision operator and link to it in a processing chain (see
section~\ref{sec_conf_proc}).

This chapter presents the base classes and interfaces LaBoGrid provides and that
can be subclassed or implemented by the user to extend LaBoGrid's capabilities.
More details are available in source code.

In order to be used, classes provided by the user must be available in JVM's
class-path.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lattice}

\verb|Lattice| element (see section~\ref{sec_conf_lbConf_latt}) provides the
name of a class implementing a lattice. This class must be a subclass of
\begin{center}
\texttt{laboGrid.lb.lattice.Lattice}
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Solid}

\verb|Solid| element (see section~\ref{sec_conf_lbConf_sol}) provides the
name of a class implementing a solid. This class must be a subclass of
\begin{center}
\texttt{laboGrid.lb.solid.Solid}
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Input and output}

\verb|Input|/\verb|Output| element (see section~\ref{sec_conf_exp_io})
provides the name of a class implementing an input/output. This class must be a
subclass of
\begin{center}
\texttt{laboGrid.ioClients.InputClient}\\
or\\
\texttt{laboGrid.ioClients.OutputClient}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Processing chain operator}

\verb|Operator| element (see section~\ref{sec_conf_proc_op}) provides the
name of a class implementing the operator. This class must be a subclass of
\begin{center}
\texttt{laboGrid.procChain.operators.LBOperator}
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Processing chain logger}
\label{sec_ext_log}

\verb|Logger| element (see section~\ref{sec_conf_proc_log}) provides the
name of a class implementing the logger. This class must be a subclass of
\begin{center}
\texttt{laboGrid.procChain.loggers.LBLogger}
\end{center}

\verb|Logger| element also provides the name of a class implementing a client
used by the logger. A class implementing a client must be a subclass of
\begin{center}
\texttt{laboGrid.procChain.loggers.client.LogClient}
\end{center}
